\documentclass[12pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amsthm,amssymb}
\usepackage{enumitem}

\newcommand{\N}{\mathbb{N}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\R}{\mathbb{R}}

\newenvironment{theorem}[2][Theorem]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{lemma}[2][Lemma]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exercise}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{corollary}[2][Corollary]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{prchk}[2][Progress Check]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{bgact}[2][Beginning Activity]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}
\newenvironment{exe}[2][Exercise]{\begin{trivlist}
\item[\hskip \labelsep {\bfseries #1}\hskip \labelsep {\bfseries #2.}]}{\end{trivlist}}

\setlength{\parindent}{0pt}

\begin{document}

\title{DuVall Final Item Exam1}
\maketitle

A proof in mathematics is a clear set of logical conclusions made about a statement that leads to the proving that the statement is either true or false. People write proofs in math to justify why certain theorems in math work the way they do. Small proofs are usually the building blocks for larger proofs that are more meaningful to a mathematician. A well written proof can help show why some mathematical anomalies exist in certain cases but not others.

I am pretty far behind in the course so far and I believe it comes from the layout of the course. I love math and have loved math for my entire school career, but something about this course has made me dread it. I feel like there is a lot of work at times, I know the work I have ahead of me to catch up on is my fault, but I think there was an overwhelming feeling from the beginning that lead me to falling behind. I understand the whole "teaching us how to teach ourselves" thing is supposed to be a good thing, but none of us will be the next Einstein. There will always be someone who is smarter than me, and there will always be someone I can lean onto for support.

\end{document}